---
title: "plotDistributions"
author: "Craig A. Wendorf"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Short Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(plotDistributions)
```

## Short Examples

### Normal Distribution

Probability Density Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,NormPDF}
norm.pdf()
norm.pdf(limits=c(1,Inf))
norm.pdf(probs=c(.025,.975))
```

Cumulative Distribution Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,NormCDF}
norm.cdf()
norm.cdf(limits=c(1))
norm.cdf(probs=c(.025,.975))
```

### Student's t Distribution

Probability Density Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
t.pdf(params=c(df=5))
t.pdf(params=c(df=5),limits=c(1))
t.pdf(params=c(df=5),probs=c(.025,.975))
```

Cumulative Distribution Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
t.cdf(params=c(df=5))
t.cdf(params=c(df=5),limits=c(2))
t.cdf(params=c(df=5),probs=c(.025,.975))
```

### F Distribution

Probability Density Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
f.pdf(params=c(df1=2,df2=10))
f.pdf(params=c(df1=2,df2=10),limits=c(3))
f.pdf(params=c(df1=2,df2=10),probs=c(.95,1))
```

Cumulative Distribution Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
f.cdf(params=c(df1=2,df2=10))
f.cdf(params=c(df1=2,df2=10),limits=c(3))
f.cdf(params=c(df1=2,df2=10),probs=c(.95,1))
```

### Studentized Range Distribution

Probability Density Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
q.pdf(params=c(nmeans=2,df=10))
q.pdf(params=c(nmeans=2,df=10),limits=c(2))
q.pdf(params=c(nmeans=2,df=10),probs=c(.95,1))
```

Cumulative Distribution Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
q.cdf(params=c(nmeans=2,df=10))
q.cdf(params=c(nmeans=2,df=10),limits=c(2))
q.cdf(params=c(nmeans=2,df=10),probs=c(.95,1))
```

### Chi Square Distribution

Probability Density Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
chisq.pdf(params=c(df=10))
chisq.pdf(params=c(df=10),limits=c(10))
chisq.pdf(params=c(df=10),probs=c(.95,1))
```
Cumulative Distribution Function plots that specify no limits, numeric limits, and probability limits, respectively.
```{r,eval=FALSE}
chisq.cdf(params=c(df=10))
chisq.cdf(params=c(df=10),limits=c(10))
chisq.cdf(params=c(df=10),probs=c(.95,1))
```
