---
subtitle: "Noncentral Beta Distribution Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Noncentral Beta Distribution Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(plotDistributions)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/plotDistributions")
}
library(plotDistributions)
```

## Noncentral Beta Distribution Examples

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

In these examples, `ncp` is the noncentrality parameter. When `ncp = 0`, the distribution reduces to the usual beta distribution, so the noncentral form is useful when you want to compare a central case against one with an added noncentral effect. For fixed `shape1` and `shape2`, increasing `ncp` pulls more density toward larger values on the 0 to 1 scale, which changes both the location and the skew of the curve.

### Probability Density Function

Get noncentral beta Probability Density Function plots using `ncp` in `params`.
```{r,nbetaPDF}
beta.pdf(params = c(shape1 = 3, shape2 = 8, ncp = 4))
beta.pdf(params = c(shape1 = 3, shape2 = 8, ncp = 4), limits = c(.2, .6))
beta.pdf(params = c(shape1 = 3, shape2 = 8, ncp = 4), probs = c(.2, .8))
```

### Cumulative Distribution Function

Get noncentral beta Cumulative Distribution Function plots using `ncp` in `params`.
```{r,nbetaCDF}
beta.cdf(params = c(shape1 = 3, shape2 = 8, ncp = 4))
beta.cdf(params = c(shape1 = 3, shape2 = 8, ncp = 4), limits = c(.2, .6))
beta.cdf(params = c(shape1 = 3, shape2 = 8, ncp = 4), probs = c(.2, .8))
```
