---
subtitle: "Noncentral Chi-Square Distribution Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Noncentral Chi-Square Distribution Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(plotDistributions)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/plotDistributions")
}
library(plotDistributions)
```

## Noncentral Chi-Square Distribution Examples

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

In these examples, `ncp` is the noncentrality parameter. When `ncp = 0`, the distribution reduces to the usual chi-square distribution. As `ncp` increases, the curve shifts to the right and becomes more spread out, so the noncentral version is useful when the central chi-square assumption is no longer appropriate.

### Probability Density Function

Get noncentral chi-square Probability Density Function plots using `ncp` in `params`.
```{r,nchisqPDF}
chisq.pdf(params = c(df = 8, ncp = 4))
chisq.pdf(params = c(df = 8, ncp = 4), limits = c(6, 14))
chisq.pdf(params = c(df = 8, ncp = 4), probs = c(.2, .8))
```

### Cumulative Distribution Function

Get noncentral chi-square Cumulative Distribution Function plots using `ncp` in `params`.
```{r,nchisqCDF}
chisq.cdf(params = c(df = 8, ncp = 4))
chisq.cdf(params = c(df = 8, ncp = 4), limits = c(6, 14))
chisq.cdf(params = c(df = 8, ncp = 4), probs = c(.2, .8))
```
